Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-21 3dpas_intro.tex

\emph{Application Dynamism: } In many scientific applications the
workflow structure is well defined, but either the components used
within this structure or the location of the data that feeds the
workflow may change dynamically.  Data coordination and planning
(identifying how data is managed from ingest through analysis to
output) within such applications can range from statically defined
interactions between execution units and data sources to a fully
adaptable interaction.  As outlined in the
Industrial Incident Notification and Response application in
(\S\ref{Kees}), the workflow structure may also change based on a user
request or the event being observed. Data relating to the coordination
of a components that make up the application can therefore also be
dynamic and change.  Exposing the data planning used within an
application makes it possible to modify or adapt it over time.

@@

\subsubsection{Understanding Distributed Dynamic Applications: }
\label{sec:quantifyingdistapps}

>>>>

\emph{Application dynamism: } In many scientific applications the
workflow structure is well defined, but either the components used
within this structure or the location of the data that feeds the
workflow may change dynamically.  Data coordination and planning
(identifying how data is managed from ingest through analysis to
output) within such applications can range from statically defined
interactions between execution units and data sources to a fully
adaptable interaction.  As outlined in the
Industrial Incident Notification and Response application in
(\S\ref{Kees}), the workflow structure may also change based on a user
request or the event being observed. Data relating to the coordination
of a components that make up the application can therefore also be
dynamic and change.  Exposing the data planning used within an
application makes it possible to modify or adapt it over time.

@@

\subsubsection{Understanding Distributed Dynamic Applications }
\label{sec:quantifyingdistapps}
